Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
Responding to reviewer comments: 4. Deep learning is used but the models are not properly explained with diagrams.

    In summary, the re-ranking model represents a significant advancement in our approach to Korean morphological analysis.
    By harnessing BERT-based models, we anticipate a notable improvement in accuracy, particularly in complex linguistic scenarios.
    The following section will detail our experimental setup and results, providing crucial empirical evidence for the effectiveness of the re-ranking model in practical applications.

>>>>

    In summary, the two-stage re-ranking model depicted within Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based re-ranking process to refine the analysis results.
    In the first stage, one BERT model is utilized to assess and re-rank the morphological paths generated by the dictionary-based analysis.
    The second stage introduces a different BERT variant, further enhancing the re-ranking accuracy by considering a diverse set of linguistic features.
    This layered approach, employing dual BERT models, is specifically designed to capture the intricacies and contextual nuances of the Korean language, addressing the challenges posed by its complex morphological structures.

    The deep learning component, particularly the BERT models, plays a pivotal role in identifying and correcting potential inaccuracies in the initial morphological analysis.
    By evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
    The experimental setup and results, detailed in the following section, provide crucial empirical evidence for the effectiveness of the re-ranking model.
    These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.
